Updated Criteria for the Diagnostic Procedure for Parkinson's Disease Dementia on Level I

### 2024-01-18 theart.qmd
citations for methods finished

---
title: "Updated Criteria for the Diagnostic Procedure for Parkinson's Disease Dementia on Level I"
shorttitle: "Parkinson's Disease Dementia Level I Criteria"
author:
  - name: Martina Kvapilova
    corresponding: false
    role:
      - Conceptualization
      - Data curation
      - Writing - original draft
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Josef Mana
    corresponding: true
    orcid: "0000-0002-7817-3978" 
    email: "josef.mana@protonmail.com"
    role:
      - Conceptualization
      - Data curation
      - Investigation
      - Formal analysis
      - Software
      - Methodology
      - Project administration
      - Validation
      - Writing - original draft
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Martin Cihak
    corresponding: false
    email: "martin.cih@gmail.com"
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Writing - original draft
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Ondrej Bezdicek
    corresponding: false
    email: "ondrej.bezdicek@gmail.com"
    role:
      - Investigation
      - Data curation
      - Funding acquisition
      - Conceptualization
      - Project administration
      - Supervision
      - Writing - original draft
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Tereza Uhrova
    corresponding: false
    email: "tereza.uhrova@vfn.cz"
    role:
      - Investigation
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Robert Jech
    corresponding: false
    orcid: "0000-0002-9732-8947"
    email: "jech@cesnet.cz"
    role:
      - Funding acquisition
      - Resources
      - Writing - review & editing
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
abstract: ""
keywords:
  - Parkinson’s disease
  - dementia
  - level I criteria
format:
 apaquarto-pdf:
   documentmode: man
   a4paper: true
   pdf-engine: lualatex
   floatsintext: false
   keep-tex: false
bibliography: references.bib
---

@@

Participants were assessed with both MMSE [@stepankova2014; @folstein1975] and MoCA [@kopecek2016]; [@nasreddine2005] to measure overall cognitive performance. Moreover, a comprehensive neuropsychological assessment was performed in accordance with MDS Task Force Level 2 criteria for MCI in PD [@litvan2012]. We described our battery including a regression based calculator for normative scores in another study [@bezdicek2017]. Besides other neuropsychological tests, the comprehensive assessment employed Clock Drawing Test (CDT) and Letter Fluency. To establish cognitive performance in individual cognitive domains according to Level 1 criteria for PDD, we used test scores proposed by [@dubois2007] and their analogues in MoCA, see Table A for details.

@@

To measure independence in activities of daily living, we administered Functional Activities Questionnaire (FAQ; [@bezdicek2011; @pfeffer1982]. To assess neuropsychiatric functioning, we used Beck Depression Inventory II (BDI-II; [@ciharova2020]; [@beck1996] and State-Trait Anxiety Inventory (STAI; Spielberg et al., 1970, @mullner1980\]. Psychotic symptoms were assessed in an interview by a trained psychiatrist.

>>>>

---
title: "Updated Criteria for the Diagnostic Procedure for Parkinson's Disease Dementia on Level I"
shorttitle: "Parkinson's Disease Dementia Level I Criteria"
author:
  - name: Martina Kvapilova
    corresponding: false
    role:
      - Conceptualization
      - Data curation
      - Writing - original draft
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Josef Mana
    corresponding: false
    orcid: "0000-0002-7817-3978" 
    email: "josef.mana@protonmail.com"
    role:
      - Conceptualization
      - Data curation
      - Investigation
      - Formal analysis
      - Software
      - Methodology
      - Project administration
      - Validation
      - Writing - original draft
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Martin Cihak
    corresponding: false
    orcid: "0000-0001-7765-4799"
    email: "martin.cih@gmail.com"
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Writing - original draft
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Ondrej Bezdicek
    corresponding: false
    orcid: "0000-0002-5108-0181"
    email: "ondrej.bezdicek@gmail.com"
    role:
      - Investigation
      - Data curation
      - Funding acquisition
      - Conceptualization
      - Project administration
      - Supervision
      - Writing - original draft
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Tereza Uhrova
    corresponding: false
    email: "tereza.uhrova@vfn.cz"
    role:
      - Investigation
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Robert Jech
    corresponding: false
    orcid: "0000-0002-9732-8947"
    email: "jech@cesnet.cz"
    role:
      - Funding acquisition
      - Resources
      - Writing - review & editing
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
abstract: ""
keywords:
  - Parkinson’s disease
  - dementia
  - level I criteria
format:
 apaquarto-pdf:
   documentmode: man
   a4paper: true
   pdf-engine: lualatex
   floatsintext: false
   keep-tex: false
bibliography: references.bib
---

@@

Participants were assessed with both MMSE [@stepankova2014; @folstein1975] and MoCA [@kopecek2016; @nasreddine2005] to measure overall cognitive performance. Moreover, a comprehensive neuropsychological assessment was performed in accordance with MDS Task Force Level 2 criteria for MCI in PD [@litvan2012]. We described our battery including a regression based calculator for normative scores in another study [@bezdicek2017]. Besides other neuropsychological tests, the comprehensive assessment employed Clock Drawing Test (CDT) and Letter Fluency. To establish cognitive performance in individual cognitive domains according to Level 1 criteria for PDD, we used test scores proposed by [@dubois2007] and their analogues in MoCA, see Table A for details.

@@

To measure independence in activities of daily living, we administered Functional Activities Questionnaire (FAQ) [@bezdicek2011; @pfeffer1982]. To assess neuropsychiatric functioning, we used Beck Depression Inventory II (BDI) [@ciharova2020; @beck1996] and State-Trait Anxiety Inventory (STAI) [@spielberg1983; @mullner1980]. Psychotic symptoms were assessed in an interview by a trained psychiatrist.
